### 2020-04-02 05-translation.tex
proof of Lemma 12 revised
and Corollary added

 \begin{restatable}[]{lemma}{lemmastruct}
 \label{lem:struct}
%\begin{lemma}
 %\label{lem:struct}
  Let ${\cal A} = (S, A)$ be a RS and let $\pi=(\gamma,\delta)$ be an extended  interactive process in ${\cal A}$. Let $P=\llbracket{\cal A},\gamma\rrbracket$ its c\CNA~translation. If $exists$ $P'$ such that $t= (P \xrightarrow{\restrict{\mathit{names}}\upsilon} P')$ is a transition of $P$, then
  \begin{enumerate}
  \item for each reaction  $a_j \in A$, the corresponding channels $r_j$ and $p_j$ appear in  $\upsilon$; for each entity $s \in S$, the corresponding channel $s$ (suitably decorated) appear in $\upsilon$; 
  the channel $\mathit{cxt}$ appears in $\upsilon$;
  %processes $P_s$ (or $\overline{P_s}$) 
%  for each  $Cxt_s$ are
 %involved in the transition $t$;
  \item for each reaction $a \in A$ and each entity $s \in S$, each virtual link offered by processes $P_a$ and $\mathit{Cxt}^1$ is  overlapped by exactly one solid link offered by  processes representing entities.
  %each process $P_s $ (or its alternative version $\overline{P}_s$), with $s \in S$, participates at most  with one solid link for each process $P_a$, and with exactly one solid link for each process $Cxt_s$.%, if $s$ is a \emph{required element} of $A_j$ in $t$.
  \end{enumerate}
  \end{restatable}

@@

>>>>

 \begin{restatable}[]{lemma}{lemmastruct}
 \label{lem:struct}
%\begin{lemma}
 %\label{lem:struct}
  Let ${\cal A} = (S, A)$ be a RS and let $\pi=(\gamma,\delta)$ be an extended  interactive process in ${\cal A}$. Let $P=\llbracket{\cal A},\gamma\rrbracket$ its c\CNA~translation. If $exists$ $P'$ such that $t= (P \xrightarrow{\restrict{\mathit{names}}\upsilon} P')$ is a transition of $P$, then
  \begin{enumerate}
  \item for each reaction  $aj \in A$, the corresponding channels $r_j$ and $p_j$ appear in  $\upsilon$; for each entity $s \in S$, the corresponding channel $s$ (suitably decorated) appear in $\upsilon$; 
  the channel $\mathit{cxt}$ appears in $\upsilon$;
  %processes $P_s$ (or $\overline{P_s}$) 
%  for each  $Cxt_s$ are
 %involved in the transition $t$;
  \item for each reaction $aj \in A$ and each entity $s \in S$, each virtual link offered by processes $P_a$ and $\mathit{Cxt}$ is  overlapped by exactly one solid link offered by  processes representing entities.
  %each process $P_s $ (or its alternative version $\overline{P}_s$), with $s \in S$, participates at most  with one solid link for each process $P_a$, and with exactly one solid link for each process $Cxt_s$.%, if $s$ is a \emph{required element} of $A_j$ in $t$.
  \end{enumerate}
  \end{restatable}

@@

The following Corollary immediately follows from Lemma~\ref{lem:struct}.

\begin{corollary}
Let ${\cal A} = (S, A)$ be a RS and let $\pi=(\gamma,\delta)$ be an extended  interactive process in ${\cal A}$. 
Let $Q=\llparenthesis{\cal A},\gamma\rrparenthesis$ and $P= \llbracket{\cal A},\gamma\rrbracket = \restrict{\mathit{names}}Q$. 
Then $P \xrightarrow{\restrict{\mathit{names}}\upsilon} P'$ iff $Q \xRightarrow{\upsilon} Q'$ and $P'=\restrict{\mathit{names}}Q'$.
\end{corollary}
